
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{roboto}

% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sami Ansari} \\ \vspace{1pt}
    \small +1 (647) 289-6889 $|$ \href{mailto:SAnsari2805@Outlook.com}{\underline{SAnsari2805@Outlook.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{https://www.linkedin.com/in/sami-ansari-205565155/}} $|$
    \href{https://github.com/7KTX}{\underline{github.com/7KTX}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cohere}{Toronto, Ontario, Canada}
      {}{}

      % Subheading for Intern of Technical Staff
      \resumeSubSubheading{Intern of Technical Staff}{Apr 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Enhanced LLM math performance by 3\% by contributing a fully synthetic post-training dataset developed without human annotation.}
          \resumeItem{Co-designed and deployed a scalable data labeling platform as part of a four-member team, efficiently processing over 100,000 continuous tasks.}
          \resumeItem{Applied advanced synthetic data generation techniques for LLM training, enhancing model accuracy and scalability.}
          \resumeItem{Implemented comprehensive benchmarking evaluations to measure and optimize LLM performance.}
          \resumeItem{Conducted model ablation studies to assess the impact of specific datasets on model performance across diverse categories.}
        \resumeItemListEnd

      % Subheading for Senior Data Quality Specialist
      \resumeSubSubheading{Senior Data Quality Specialist}{May 2023 -- Apr 2024}
        \resumeItemListStart
          \resumeItem{Engineered advanced Python applications to audit and analyze over 40,000 tasks, uncovering critical insights and complex data labeling patterns that informed machine learning model enhancements.}
          \resumeItem{Directed a team of over 200 AI annotators, cultivating a culture of excellence and implementing best practices that elevated data quality and annotation accuracy.}
          \resumeItem{Spearheaded the development of an innovative ticketing system, streamlining feedback to AI annotators and boosting overall data quality.}
          \resumeItem{Championed and executed AI annotation best practices, optimizing workflows and enhancing LLM performance.}
          \resumeItem{Recognized for delivering pivotal insights that improved LLM performance within data quality operations.}
          \resumeItem{Maintained and strengthened strategic vendor relationships, resolving complex queries on STEM and code data quality and styling to ensure consistent data standards.}
          \resumeItem{Devised and implemented comprehensive assessment criteria for AI Data Trainer recruitment, enhancing candidate selection effectiveness.}
          \resumeItem{Proctored and evaluated AI Data Trainer assessments, contributing to the onboarding of high-caliber talent.}
          \resumeItem{Continuously expanded expertise in AI and LLM behaviors to enhance strategic decision-making.}
        \resumeItemListEnd

      % Subheading for Data Quality Specialist
      \resumeSubSubheading{Data Quality Specialist}{May 2023 -- May 2023}
        \resumeItemListStart
          \resumeItem{Enhanced language model capabilities by spearheading data quality improvement initiatives.}
          \resumeItem{Delivered critical annotations and insights that boosted LLM performance.}
          \resumeItem{Leveraged advanced tools and platforms to rigorously uphold data quality standards.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{Toronto, Ontario}
      {Bachelor of Science in Computer Science and Mathematics}{Sep. 2017 -- May 2022}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI Data Annotation Platform} $|$ \emph{Python, JavaScript, React, Firebase}}{Jan 2024 -- Oct 2024}
          \resumeItemListStart
            \resumeItem{Developed and maintained a full-stack web application to streamline AI data annotation processes.}
            \resumeItem{Implemented a user-friendly frontend with React and managed backend services using Firebase.}
            \resumeItem{Optimized data handling and storage with Firestore for efficient retrieval and scalability.}
            \resumeItem{The project's success contributed to receiving multiple machine learning internship offers.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, Bash} \\
     \textbf{Frameworks}{: FastAPI, Streamlit, Dask, Polars, Pandas, Pydantic, Graphviz, Sympy, Redis, DuckDB, JAX, Reactivex} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, VS Code, PyCharm, Neovim} \\
     \textbf{Libraries}{: NumPy, Matplotlib, requests, rich, click, inquirer, cohere, wandb, plotly, nltk, faker, tokenizers}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
